---
title: "My Report"
author: "Tim Wetzel"
date: "5/29/2019"
output: html_document
---

```{r global_options, echo=FALSE}
knitr::opts_chunk$set(warning = FALSE, fig.path = "figs/")
```


# Heading

## Subheading

### Smaller Heading

*This is some formatting*

**Some other formatting**

[A hyperlink](https://google.com)

- A bulleted list
- Another list item

1. This is a numbered list with bullets embedded
  - First entry
  - Second entry
  - Third entry
1. This will hopefully be number 2

~~This was a bad item~~

```{r load_data, results = "hide"}
library("gapminder")
library("ggplot2")
suppressPackageStartupMessages(library(tidyverse))
data(gapminder)
head(gapminder)
```


```{r gdp_lifeexp_plot, fig.width = 4, fig.height = 4}
ggplot(data = gapminder, mapping = aes(x = gdpPercap, y = lifeExp)) + geom_point()
```

Here, we see the plot for life expectancy as time progresses.

```{r lifeexp_v_time}
ggplot(data = gapminder, mapping = aes(x = year, y = lifeExp)) + geom_point()
```

The largest population of any country in this data set is `r max(gapminder$pop)`.

```{r iceland, echo = FALSE}
iceland = dplyr::filter(gapminder, country == "Iceland")
max_iceland_lifeexp = max(iceland$lifeExp)
```

The maximum life expectancy in Iceland is `r max_iceland_lifeexp`.

```{r tanzania, echo = FALSE}
tanzania = dplyr::filter(gapminder, country == "Tanzania")
mean_lifeexp_tanz = mean(tanzania$lifeExp)
std_dev_lifeexp_tanz = sd(tanzania$lifeExp)
```

For Tanzania, the average life expectancy is `r mean_lifeexp_tanz`, while the standard deviation is `r std_dev_lifeexp_tanz`.

```{r}
ggplot(data = gapminder, mapping = aes(x = year, y = pop)) + geom_point()
```

Here is some more text that I am adding.
